Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-12 analysis/paper/paper.Rmd
Minor edits to analysis section

Disease severity was converted to area under the disease progress stairs (AUDPS) [@simko2012area]. As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using multivariate generalised linear mixed models implemented in the MCMCglmm package [@MCMCglmm2017] in R [@R2018].

>>>>

Disease incidence and severity were converted to area under the disease progress stairs (AUDPS) [@simko2012area]. As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using multivariate generalised linear mixed models implemented in the MCMCglmm package [@MCMCglmm2010] in the R programming environment [@R2018].
